### 2013-06-04 MSWL_ECO_lesson1.tex
Delete section part II in lesson 1
Revision chapter 1

@@

@@

@@

A video was played in class to demonstrate the new paradigm around Internet. The most important conclussions after watching are:\\
1) Crowdsourcing: Multiple people doing something. New economic value.\\ 
2) It is difficult to start some kind of projects (Radio, Television, Newspaper, etc.).\\ 
3) In other similar markets (super-computer), some time (2002), the biggest supercomputer was SETTI program (were thousands of contributors supplied his limited resources).\\
4) Things are changing: Wikipedia, Apache, are FLOSS success stories.\\
5) Crowdsourcing (SETI): it is something that can be very huge, involving many people, and done via Internet, by means different from states or big companies.\\
6) Computer Market is high advanced, Computers are cheap and gives you freedom to:\\
- Do whatever you want with it.\\
- Share it to do other things, help others.\\
7) The most collaborative company might be Google. Google page rank algorithm takes into account what the rest of the people consumes, and what the rest of the people link. They won Open-Directory (Free Software). They take profit of what people does not value, or what people want to do.\\
There are cases as Google Goggles or Scanning words projects in Captchas.\\
\\
\begin{tabular}{| l | c | r |}
   \hline
   & Market Based & Non-Market Based \\
   \hline
   Decentralized  & Price Based    & \textbf{Social Sharing/Exchange} \\
   \hline
   Centralized    & Firm Hierarchy & Government/non profits (NGOs) \\
   \hline
\end{tabular}
\\
\\
(*1)In past time this paradigm was used for small projects (look after of a garden in a neighbourhood)\\
It is normally valid for "non-material" things, changing the sense of property. That happens on software, music, etc.\\
Non-market decentralized models need new means of coordination.\\
Means competition: (FLOSS vs Microsoft, Skype vs Telecomms, Wikipedia vs Encyclopedias, etc.)
The results of the competition means also the kind of the society we will live.

\section{Part II}\label{Part II} % TODO: Change for properly section title.

\section{Conclusions}\label{conclusions}

>>>>

\begin{figure}[htb]
	\begin{center}
		\includegraphics{webServer1303}
		\caption{Web Server share market}
		\label{fig:webServer1303}
	\end{center}
\end{figure}

@@

\begin{figure}[htb]
	\begin{center}
		\includegraphics{mobile_tablet_browser}
		\caption{Mobile-Tablet browser}
		\label{fig:mobile_tablet_browser}
	\end{center}
\end{figure}

@@

\begin{figure}[htb]
	\begin{center}
		\includegraphics{Operating_systems_used_on_top_500_supercomputers}
		\caption{Operatingvsystems used on top 500 supercomputers}
		\label{fig:Operating_systems_used_on_top_500_supercomputers}
	\end{center}
\end{figure}

@@

A video was played in class to demonstrate the new paradigm around Internet. The most important conclussions after watching are:\\
1) Crowdsourcing: Multiple people doing something. New economic value.\\ 
2) It is difficult to start some kind of projects (Radio, Television, Newspaper, etc.).\\ 
3) In other similar markets (super-computer), some time (2002), the biggest supercomputer was SETTI program (were thousands of contributors supplied his limited resources).\\
4) Things are changing: Wikipedia, Apache, are FLOSS success stories.\\
5) Crowdsourcing (SETI): it is something that can be very huge, involving many people, and done via Internet, by means different from states or big companies.\\
6) Computer Market is high advanced, Computers are cheap and gives you freedom to:\\
- Do whatever you want with it.\\
- Share it to do other things, help others.\\
7) The most collaborative company might be Google. Google page rank algorithm takes into account what the rest of the people consumes, and what the rest of the people link. They won Open-Directory (Free Software). They take profit of what people does not value, or what people want to do.\\
There are cases as Google Goggles or Scanning words projects in Captchas.\\
\\
\begin{tabular}{| l | c | r |}
   \hline
   & Market Based & Non-Market Based \\
   \hline
   Decentralized  & Price Based    & \textbf{Social Sharing/Exchange} *\\
   \hline
   Centralized    & Firm Hierarchy & Government/non profits (NGOs) \\
   \hline
\end{tabular}
\\
\\
(*)In past time this paradigm was used for small projects (look after of a garden in a neighbourhood)\\
It is normally valid for "non-material" things, changing the sense of property. That happens on software, music, etc.\\
Non-market decentralized models need new means of coordination.\\
Means competition: (FLOSS vs Microsoft, Skype vs Telecomms, Wikipedia vs Encyclopedias, etc.)
The results of the competition means also the kind of the society we will live.

\section{Conclusions}\label{conclusions}
The evidence from the study of the market numbers suggests that the number of FLOSS projects has grown exponentially at least years, so FLOSS market is not an insignificant market. There are niches where the lead product are free software and it is really stable market, and is difficult to change for privative software.
\\
Nowadays, free software is sometimes the best option in certain business and sometimes not, but the important thing to note is that almost all companies are considering free software strategies on their global business plans. 
\\
It is important to consider that internet is changing the model. Many actors now have the tool to be interconected and is used to synchronise people in a very efficient way. A new paradigm in internet springs up strongly upwards. Around this new concepts appear like crowdsourcing, which is an online, distributed requirement solving and production mode, and not only for software production.
